\subsection{Scope}

This research undertaken as part of this module, attempted to assess if website log files had sufficient data for a formula to be applied to detect attacks. Part of the scope was to collect a representative sample of real-world data, to measure the effectiveness of the proposed methodology. The use of this sample proved it is more accurate when validating security models; therefore, challenging conventional thinking that studies have to generate their own data.

Given the novel nature, the scope of this work was correct due to the novel nature of the work. This was compounded by the difficulty I had getting ethical approval, which will be explored in a later section. Even given these challenges, I was able to gather enough data to test my hypothesis. The methodology was tested on a local website and could be applied to any across the world. The variables associated with increased risk, such as country of origin, were controlled for. However, due to countries' differing internet patterns, this technique may be hard to generalise to a global scale, especially for a pilot study.


%Mention research has not been attempted by others in the field.

\subsection{Objectives}

The objectives in my proposal were to; identify how attacks are evading current techniques, understand attack characteristics and refine a formula that can detect and determine risk. The high accuracy of the formula indicates I have understood current attacks and their evasion techniques proving a successful detection methodology. Although, I had to remove an objective, which would have been to develop a better way to assign risk to a country. I intended to look at the number of attacks coming from IP addresses within a country compared to the size of the population. But, I was unable to achieve this. Also, this data is difficult to determine. Another reason for its removal was that I was unable to contact the lecturer who suggested this idea, because they now work at another university. Therefore, I kept the original methodology used in the previous research, which still was able to prove that looking at risk for a country is a valid factor to consider.

\subsection{Risk}

Due to the sensitive nature of the data, I identified the risk that website owners may be unwilling to give me their data for analysis. However, after engaging with them, they were happy to do so. The research could potentially inform them of attacks on their website; if any happened to be found, I could advise them on how they could be mitigated. The biggest risk associated with this project was the lack of previous literature. There was a question in my mind that, as this methodology seemed relatively straight-forward, why had nobody tried this before? Was it because it was unsuccessful? This risk was mitigated due to the fact that, even if the conclusion did not support my hypothesis I would still be adding knowledge to this field. Therefore, this was a worthwhile risk and one that I would gladly take again.