\cite{thurow1999dynamics} discusses the benefits of multidisciplinary research teams using grounded theory. He argues that more complex challenges can be solved by using a composite team of multiple disciplines. This is why working with Nick (a Computer Science lecturer) allowed us to solve multi-faceted problems, in particular, the research undertaken for this module.

I could have worked with a cybersecurity lecturer, however this may have held the research back as they may not have wanted to alienate their peers and they may not have wanted to risk trying a new methodology that does not conform to the research status quo. Literature suggests that scientists in a given fielf may be prejudiced purely because of their belief in a scientific theory to commitment to their own findings. Because me and Nick work in different fields, we had the best interests of the research at heart https://www.ncbi.nlm.nih.gov/pmc/articles/PMC1182327/
 Myself and Nick both work in the computer science sector, however we have different specialisms within this domain. Thus, having complimentary skill-sets that enabled a multidisciplinary approach; focussing on different areas of the research. Nick used his knowledge of programming algorithms to help improve the formula. Whilst, I focussed on aspects of the data pertaining to cyber-security. Hence, I was able to identify risk factors and Nick would then advise on how to efficiently calculate any risk attached to the data. For example, I determined user agents could be an identifier of risk,  originally trying a Levenshtein distance to find the nearest user agent. This approach proved unsuccessful, a danger of it was it may have resulted in misidentification of user agents due to their similarities. However, Nick suggested doing a bag of words approach, which was ultimately a stronger and more accurate methodology. This stopped me overcomplicating the detection of user agents. Working with Nick has taught me that sometimes simpler methodologies may have better results and by over-complicating programs it may become harder to achieve the desired result.

%Furthermore, Nick had prior knowledge of the project, due to supervision at undergraduate level and therefore understood the project and its complexities. 

Looking back on this project, working with Nick was enjoyable, due to our different approaches. Nick always had a positive outlook on the project and its challenges; therefore keeping my motivation high alongside my belief in the project having merit. Nick also contributed ideas to the project and helped in implementing them. This reduced stress on me and he enabled greater faith in our methodology. However, a slight problem was, Nick was difficult to reach at times. The primary way to ask a question to him was looking for a space in his calendar that was mutually convenient. I often felt bad for booking in meetings for issues that could have been solved via email but, this was unavoidable. Sometimes it was impossible to get meetings with Nick for 2-3 weeks if he was fully booked. The inability to contact Nick at times added to my stress, particularly at key times; for example, when submitting my ethics for the third time. I was going to wait for Nick to double-check, but I was getting more stressed about the ethics not coming back on time; rather than the potential of it being rejected for the fourth time for problems Nick may have spotted. Additionally, I found the inability to make contact with someone added to my stress. This was particularly apparent when I was not on campus in semester one, so I could not even go to Nicks office. Overall, working with Nick proved beneficial and if I were to do a similar project I would ensure we had better communication outside of meetings if possible.

%The project was a sole effort, there was no instated leader, however, project management strategies were adopted in order to monitor and assure the completion of this quality project (\cite{visser1990expert}). Through building a framework with the option for additional modules to be added, I learned that I have competence as a project leader in terms of project management. The time management of the project was well overseen and time critical elements were put in place, however, the use of a GANTT chart was considered unfitting for the project. AJ Shenhar states that, \textit{"project management differs with the kind of project, and that management style, attitude, and practice must be adapted to the specific project type"} (\cite{Shenhar1}; 33). In short this means that different projects require different management styles. Using this project as an example, not having an initial GANTT chart led to a more agile approach.

%In a team related project there may have been issues regarding the overall build of the software including the login screen. An article by \citeauthor{GanttPRO} discusses the 10 major pitfalls in team based project management, one of the pitfalls being; setting unrealistic deadlines. (\cite{GanttPRO}). This may have lead to overall communication problems and further compatibility issues for adding further module content, due to deadlines not being met and the delay of the project. A great deal of skill development around project management would have to be achieved, especially with time management and communication skills.

%Keeping us both informed as to where the research was and what needed to be undertaken for the following week
%Throughout the year our techniques were critically evaluated. We developed a habit of meeting near weekly, therefore maintaining momentum in the research overall. Despite this, there were still points where progress was slow. Making me feel like I hadn't achieved much, negatively impacting my motivation. The project was not initially planned out, naturally generating a more agile approach. Furthermore, due to the novel nature of the work there was a danger that I would set unrealistic deadlines in order to complete the research; this is evidenced by times where methodologies had to be redesigned due to the lack of previous research. One of the ten major pitfalls of projects success(\cite{GanttPRO}) is setting unrealistic deadlines as deemed by \citeauthor{GanttPRO}. The agile approach yielded results because I had to deal with additional complication. The level of support I require was not met for an elongated period of time, making it difficult to plan activities which could be undertaken in advance. Once, I received a phone call at 6pm, informing me I could come into University the next day. This is an example showing I had varying amounts of time to work each week. In addition to this, I also had times were I thought I would be in and would find out that I could not attend. This meant some of our meetings had to take place on Teams and sometimes involved brainstorming on whiteboards. This was sometimes difficult to read, if internet connection was poor. On reflection the whiteboard feature on Teams may have been better; also, I should have tried to get more support online, if not in person. The circumstances dictated this work required a different approach to manage the project. This is inline with AJ Shenhar's theory on project management (\cite{Shenhar1}), who suggests that different projects require different styles of management. So due to external factors an agile project management style was needed.

AJ Shenhar suggests that different projects require different styles of management (\cite{Shenhar1}). The research undertaken required very little project management in the traditional sense, due to the small team involved. By using an unplanned, agile methodology I was still able to deliver a well-rounded research project. This also led to a high degree of being able to question each stage of the project, because we were not rushing to hit deadlines. This is further backed up by \citeauthor{GanttPRO} who suggest that setting unrealistic deadlines is one of the  major pitfalls of projects success. Given varying levels of support offered to me throughout the year, it was important that I kept setting realistic weekly deadlines. By engaging as regularly as possible with Nick he was able to critically evaluate my proposed methodology; leading to a robust exchange of views. This also helped me write the paper, as it forced me to concisely explain my thought processes in a clear way and see where the pitfalls of the methodology may be, so I could address these in the paper. Some meetings with Nick only lasted an hour, which when trying to talk over complex areas of code may have been too short. This was compounded by poor internet connection that sometimes made communication difficult.

%This occurred organically in the present research as ideas could be effectively implemented without disagreement, regarding the direction of the project.

%needs further reflection

The work was a follow-on from my undergraduate dissertation. Most of the underlying software was already written, therefore I worked to identify small improvements that could be made. Then developing a methodology to assess the accuracy of the program. However, new ideas from different researchers may have led to a better outcome, because of the opportunity for collaboration. It can be shown that the more collaboration that exists in research projects, the higher the quality of the research (\cite{figg2006scientific}). Therefore the collaboration within this project led to a better output but other collaborators might have increased this further. Myself and Nick would often challenge one another's ideas in order to ensure our methodology was robust. It may have been useful to include another cyber security researcher, in order to further challenge our thinking. Additionally, when classifying the accuracy of the program; having someone to classify the data as well, helping to remove any bias that I might have had. However, I did get a high degree of collaboration with Nick; this is in line with Robert E. Levasseur (2010) who states "to initiate and... the high level of two-way communication" (\cite{levasseur2010people}). The initiation process occurred very naturally between myself and Nick. While on placement, we discussed a problem caused by an IP address attacking my website and I proposed that I program something to detect the attack. This sparked a reciprocal flow of ideas that continued throughout the research, even if some elements were absent from the final project. 

Throughout this project, there have been many stages where reflection has been needed in order to understand the progress that has been made. By regularly putting my research on hold and taking a step back, I was able to develop a regular reflective habit  (\cite{dyment2010quality}). For example, after making changes to the formula, I would run the data again and reflect on the output. However, at other times throughout the year, there have been ongoing issues with a lack of available support in order to complete work. It added more stress and I often felt like I was rushing work that I should have taken more time over. There have been periods where reflection in action have been required, often when doing this we are unaware that we have derived meaning from an experience. Through this process we find ourselves doing the same action again, as it has a positive outcome (\cite{Schon83}). When I reflected on where I was in the project, and what I needed to do to progress it resulted in more effective decision making and problem solving. This was mainly evident by last minutes changes made to my proposal. This meant having to do an online zoom session, so that someone was able to assist me in completing my final draft. The positive outcome here was that I got the work done and I was able to learn that doing work on zoom, although not ideal, still contributed to the success of the project. One thing I've learnt is, not asking other people to proofread my work near the deadline at risk of being too last minute to get any meaningful changes in. This is an example of how I am putting Bourner's theory of reflection, being the experience of turning reflection into learning in action (\cite{bourner2003assessing}).

 


%The initiation for this project was started while I was on placement. I chatted to Nick about a problem that I was having with an IP address attacking my website and made a comment about 'I should be able to programme something to identify the attack'. Nick then started drawing some user interfaces that didn't end up coming into the final project. However this initiation felt very natural and began some good two way communication with ideas flowing backwards and forwards, and set us up for good communication backwards and forewords due to the fact we both felt invested in the project and when communicating, we allowed each other space to come up with new ideas.
% However, this research has never been undertaken before; it may have been hard for new people to come in and understand the research.


%If this had been an entirely new project it would have been beneficial to collaborate with more than one person. To bring in new ideas and a different point of view. However due to the fact that it was a continuation I believe it was the right decision to do it on my own.  